\documentclass[12pt, titlepage]{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=blue,
    filecolor=black,
    linkcolor=red,
    urlcolor=blue
}
\usepackage[round]{natbib}
\usepackage{float}
\usepackage{pdflscape}
\usepackage{longtable}
\usepackage{multirow}
\usepackage[shortlabels]{enumitem}

\input{../Comments}
\input{../Common}

\begin{document}

\title{System Verification and Validation Plan for \progname{}}
\author{\authname}
\date{\today}

\maketitle

\pagenumbering{roman}

\section{Revision History}

\begin{table}[hp]
	\caption{Revision History} \label{TblRevisionHistory}
	\begin{tabularx}{\textwidth}{llX}
		\toprule
		\textbf{Date}    & \textbf{Developer(s)} & \textbf{Change}                                      \\
		\midrule
		October 26, 2022 & Arkin Modi            & Added Software Validation Plan                       \\
		October 27, 2022 & Joy Xiao              & Add Testing Team and Design Verification             \\
		October 27, 2022 & Arkin Modi            & Add Automated Testing and Verification Tools         \\
		October 28, 2022 & Timothy Choy          & Add Relevant Documentation                           \\
		October 28, 2022 & Leon So               & Add Summary                                          \\
		October 28, 2022 & Arkin Modi            & Add System Tests for Quotes                          \\
		October 29, 2022 & Leon So               & Add Objectives                                       \\
		October 29, 2022 & Arkin Modi            & Add System Tests for Work Orders                     \\
		October 29, 2022 & Joy Xiao              & Add System Tests for Appointments                    \\
		October 30, 2022 & Timothy Choy          & Add SRS Verification Plan                            \\
		October 30, 2022 & Leon So               & Add Operational and Environmental Tests              \\
		October 30, 2022 & Arkin Modi            & Add Implementation Verification Plan                 \\
		October 30, 2022 & Leon So               & Add Usability and Humanity Tests                     \\
		October 30, 2022 & Joy Xiao              & Add System Tests for Services                        \\
		October 30, 2022 & Leon So               & Add System Tests for Employee Management             \\
		October 30, 2022 & Arkin Modi            & Add Look and Feel System Tests                       \\
		October 30, 2022 & Arkin Modi            & Add Security System Tests                            \\
		October 31, 2022 & Timothy Choy          & Add System Tests for Shop Lookup                     \\
		October 31, 2022 & Joy Xiao              & Add Cultural Requirements Tests                      \\
		October 31, 2022 & Timothy Choy          & Add System Tests for Shop Profile                    \\
		October 31, 2022 & Timothy Choy          & Add Performance Tests                                \\
		October 31, 2022 & Leon So               & Add System Tests for Authentication                  \\
		November 1, 2022 & Timothy Choy          & Add System Tests for Employee Profile                \\
		November 1, 2022 & Timothy Choy          & Add Maintainability and Support Tests                \\
		November 1, 2022 & Timothy Choy          & Add VnV Verification Plan                            \\
		November 1, 2022 & Joy Xiao              & Add Legal Requirement Tests                          \\
		November 1, 2022 & Arkin Modi            & Add Traceability Between Test Cases and Requirements \\
		November 2, 2022 & Timothy Choy          & Add Introductory Blurbs                              \\
		November 2, 2022 & Arkin Modi            & Add reflection                                       \\
		November 2, 2022 & Joy Xiao              & Add reflection                                       \\
		November 2, 2022 & Leon So               & Add reflection                                       \\
		November 2, 2022 & Timothy Choy          & Add reflection                                       \\
		March 1, 2023    & Arkin Modi            & Add Unit Tests for User Module                       \\
		March 1, 2023    & Arkin Modi            & Add Unit Tests for Quotes Module                     \\
		March 1, 2023    & Arkin Modi            & Add Unit Tests for Appointments Module               \\
		March 1, 2023    & Arkin Modi            & Add Unit Tests for Work Orders Module                \\
		March 1, 2023    & Arkin Modi            & Add Unit Tests for Services Module                   \\
		\bottomrule
	\end{tabularx}
\end{table}

\newpage

\tableofcontents

\listoftables

\listoffigures
% \wss{Remove this section if it isn't needed}

\newpage

\section{Symbols, Abbreviations and Acronyms}

\renewcommand{\arraystretch}{1.2}
\begin{tabular}{l l}
	\toprule
	\textbf{symbol} & \textbf{description}                \\
	\midrule
	CI              & Continuous Integration              \\
	HA              & Hazard Analysis                     \\
	HTTP            & Hypertext Transfer Protocol         \\
	MG              & Module Guide                        \\
	MIS             & Module Interface Specification      \\
	PWA             & Progressive Web Application         \\
	SRS             & Software Requirements Specification \\
	VnV             & Verification and Validation         \\
	\bottomrule
\end{tabular}\\

\newpage

\pagenumbering{arabic}

This document outlines the verification and validation of Sayyara. Within this document, there will
be plans for verifying the SRS document, the design plan, the VnV plan, the implementation plan,
and the software plan. This document will also list the methods of testing that we plan to use.
Furthermore, this document will list specific system and unit tests as described in our Functional
and Nonfunctional requirements in the SRS, and the modules in the MG and MIS.
% \wss{provide an introductory blurb and roadmap of the Verification and Validation plan}

\section{General Information}

\subsection{Summary}

Sayyara is a Progressive Web Application (PWA) which acts as a single platform for independent auto
repair shops and vehicle owners. This platform allows independent auto repair shops and vehicle
owners to interact in various ways. Using Sayyara, vehicle owners can search for auto repair shops
and services based on a variety of search filters; request quotes for service; book, view, and
manage service appointments. On the application, auto repair shop owners have full shop management
capabilities such as: adding and managing a list of employees; managing a list of service types and
corresponding service appointment availabilities; managing store information such as location,
hours of operation, and contact information. Auto repair shop owners and employees will be able to
manage quotes, service appointments, and work orders from a single application.

\subsection{Objectives}

The objective of the testing outlined in this document is to demonstrate adequate usability and
ensure that the system is in a functional state for the end users. The testing and validation will
also aid in ensuring that the product fulfills the system requirements, intended use, and goals of
stakeholders.

\subsection{Relevant Documentation}

Below are the relevant documents that will be referred to in the VnV Plan.

\begin{itemize}
	\item \href{https://github.com/arkinmodi/project-sayyara/blob/main/docs/DevelopmentPlan/DevelopmentPlan.pdf}{Development Plan \citep*{DevPlan}}
	\item \href{https://github.com/arkinmodi/project-sayyara/blob/main/docs/HazardAnalysis/HazardAnalysis.pdf}{Hazard Analysis \citep*{HA}}
	\item \href{https://github.com/arkinmodi/project-sayyara/blob/main/docs/Design/MG/MG.pdf}{Module Guide \citep*{MG}}
	\item \href{https://github.com/arkinmodi/project-sayyara/blob/main/docs/Design/MIS/MIS.pdf}{Module Interface Specification \citep*{MIS}}
	\item \href{https://github.com/arkinmodi/project-sayyara/blob/main/docs/SRS/SRS.pdf}{Software Requirements Specification \citep*{SRS}}
\end{itemize}

% \wss{Reference relevant documentation.  This will definitely include your SRS
% 	and your other project documents (design documents, like MG, MIS, etc).  You
% 	can include these even before they are written, since by the time the project
% 	is done, they will be written.}

\section{Plan}

The following section will cover our plan to verify and validate certain components of our project.
We will include the members responsible for the verification and validation, as well as our plans
to verify the SRS, design plan, VnV plan, implementation plan, automated testing and verification
tools, and software plan.

% \wss{Introduce this section.   You can provide a roadmap of the sections to
% 	come.}

\subsection{Verification and Validation Team}

The verification and validation team will consist of the core developers (Joy Xiao, Tim Choy, Leon
So, Arkin Modi), as well as the course instructor and TAs.

The developers are responsible for coming up with tests with suitable edge cases to evaluate the
correctness of Sayyara. The developers will all be responsible for writing and executing all test
cases listed in the document and taking note of the results. The developers will ensure that
Sayyara passes all tests after performing the tests and making any necessary updates.

\subsection{SRS Verification Plan}

SRS verification will be done by the core developers of the project, as well as by the TAs of the
course. To verify the contents of the
\href{https://github.com/arkinmodi/project-sayyara/blob/main/docs/SRS/SRS.pdf}{SRS}, we will
compare the requirements stated by the stakeholder, Nabeel, with the requirements stated in the
SRS. Furthermore, we will show our SRS to Nabeel for their review. We believe that this is
sufficient to verify the SRS, as Nabeel has defined clear requirements for the project.

% \wss{List any approaches you intend to use for SRS verification.  This may include
% 	ad hoc feedback from reviewers, like your classmates, or you may plan for
% 	something more rigorous/systematic.}

% \wss{Maybe create an SRS checklist?}

\subsection{Design Verification Plan}

Design verification will be done by the core developers of the project. The design will also be
reviewed by the TAs of the course. The design of the system will be verified by going through the
requirements from the
\href{https://github.com/arkinmodi/project-sayyara/blob/main/docs/SRS/SRS.pdf}{SRS} and determining
whether the outputs correspond with the expected inputs. The verification will also be done by
going through the
\href{https://github.com/arkinmodi/project-sayyara/blob/main/docs/Design/MG/MG.pdf}{MG} and
\href{https://github.com/arkinmodi/project-sayyara/blob/main/docs/Design/MIS/MIS.pdf}{MIS}
checklist and ensure that all the modules are completed and fulfill the corresponding requirements.

\subsection{Verification and Validation Plan Verification Plan}

The VnV Plan verification will be done by the core developers of the project, and the TAs of the
course. To verify the plan, we will run through the requirements stated in the
\href{https://github.com/arkinmodi/project-sayyara/blob/main/docs/SRS/SRS.pdf}{SRS} and match every
requirement to at least one test. Regarding the unit tests, we will match each module stated in the
\href{https://github.com/arkinmodi/project-sayyara/blob/main/docs/Design/MG/MG.pdf}{MG} and
\href{https://github.com/arkinmodi/project-sayyara/blob/main/docs/Design/MIS/MIS.pdf}{MIS} to the
tests written in the VnV plan.

% \wss{The verification and validation plan is an artifact that should also be verified.}

% \wss{The review will include reviews by your classmates}

% \wss{Create a checklists?}

\subsection{Implementation Verification Plan}

Automated integration tests will be created to fulfill the system tests defined in section
\ref{System Test Description} and automated unit tests will be created to fulfill the tests defined
in section \ref{Unit Test Description}. Static analysis will be performed through code review by at
least one core team member per pull request and automation tools as stated in \ref{Automated
	Testing and Verification Tools}. A pull request will cover at most one module.

Manual System Tests defined in section \ref{System Test Description} shall take place from January
16, 2023 to January 30, 2023. The areas of responsibility will be divided as described in table
\ref{Manual System Testing Responsibilities}.

Due to the large scope of this project and the timeline constraints, the team has chosen to rely
more heavily on manual testing instead of investing in learning a new end-to-end testing framework
and building a large fully featured test suite.

\begin{table}[H]
	\centering
	\caption{Manual System Testing Responsibilities}
	\vspace{5pt}
	\begin{tabular}{|p{0.5\textwidth}|p{0.5\textwidth}|}
		\hline
		\textbf{Area of Testing} & \textbf{Team Member Responsible} \\
		\hline
		Authentication           & Leon So                          \\
		\hline
		Appointments             & Joy Xiao                         \\
		\hline
		Quotes                   & Arkin Modi                       \\
		\hline
		Work Orders              & Arkin Modi                       \\
		\hline
		Employee Management      & Leon So                          \\
		\hline
		Services                 & Joy Xiao                         \\
		\hline
		Shop Lookup              & Timothy Choy                     \\
		\hline
		Shop Profile             & Timothy Choy                     \\
		\hline
		Employee Profile         & Timothy Choy                     \\
		\hline
	\end{tabular}

	\label{Manual System Testing Responsibilities}
\end{table}

\subsection{Automated Testing and Verification Tools} \label{Automated Testing and Verification Tools}

All tooling and automations that will be used for testing and verification have been documented in
the
\href{https://github.com/arkinmodi/project-sayyara/blob/main/docs/DevelopmentPlan/DevelopmentPlan.pdf}{Development
	Plan} under the ``Technology'' and ``Code Standard'' sections.

As part of our CI, we will have a pipeline running the automated tests against every commit to the
main branch and every pull request opened against the main branch that contains a source code or
testing code change. There will also be a pipeline running against every pull request asserting
adherence to the documented code style standards. Code coverage reports will be commented directly
to the pull request or the commit to the main branch using a pipeline.

\subsection{Software Validation Plan}

The plan for validating the software and the requirements shall be to conduct review session with
the stakeholders. These review sessions shall focus on the business events and user flows as
defined in the \href{https://github.com/arkinmodi/project-sayyara/blob/main/docs/SRS/SRS.pdf}{SRS}.

\section{System Test Description} \label{System Test Description}

\subsection{Tests for Functional Requirements} \label{Tests for Functional Requirements}

The following system tests are for functional requirements, as defined in the
\href{https://github.com/arkinmodi/project-sayyara/blob/main/docs/SRS/SRS.pdf}{SRS}. To ensure all
requirements are covered, the subsections for the VnV plan match the subsections in the SRS.
Furthermore, each test case will have a label linked to their respective business event.

% \wss{Subsets of the tests may be in related, so this section is divided into
% 	different areas.  If there are no identifiable subsets for the tests, this
% 	level of document structure can be removed.}

% \wss{Include a blurb here to explain why the subsections below
% 	cover the requirements.  References to the SRS would be good here.}

\subsubsection{Authentication}
This section will contains tests covering the ``Authentication'' requirements defined in the
\href{https://github.com/arkinmodi/project-sayyara/blob/main/docs/SRS/SRS.pdf}{SRS}.

\begin{enumerate}

	\item \textbf{FRT-BE1-1}

	      Control: Manual

	      Initial State: Customer with no existing account

	      Input: Customer submits sign up form with valid email, password, name, and phone number

	      Output: Redirect to vehicle owner landing page upon successful registration

	      Test Case Derivation: New customer wants to sign up for a new account with valid sign up
	      information provided

	      How test will be performed: The tester will register and sign up for a new customer account using
	      valid sign up information

	\item \textbf{FRT-BE1-2}

	      Control: Manual

	      Initial State: Shop owner with no existing account

	      Input: Shop owner submits sign up form with valid email, password, name, phone number, shop name,
	      shop address, and shop phone number

	      Output: Redirect to shop owner landing page upon successful registration

	      Test Case Derivation: New shop owner user wants to sign up for a new account with valid sign up
	      information provided

	      How test will be performed: The tester will register and sign up for a new shop owner account using
	      valid sign up information

	\item \textbf{FRT-BE1-3}

	      Control: Manual

	      Initial State: Employee with no existing account

	      Input: Employee submits sign up form with valid email, password, name, and phone number

	      Output: Redirect to employee landing page upon successful registration

	      Test Case Derivation: New employee user wants to sign up for a new account with valid sign up
	      information provided

	      How test will be performed: The tester will register and sign up for a new employee account using
	      valid sign up information

	\item \textbf{FRT-BE2-1}

	      Control: Manual

	      Initial State: Customer with existing account and not logged in

	      Input: Customer submits login form with valid email and password

	      Output: Redirect to vehicle owner landing page upon successful login

	      Test Case Derivation: Customer wants to login to existing with valid login credentials provided

	      How test will be performed: The tester will login to an existing customer account using valid login
	      credentials

	\item \textbf{FRT-BE2-2}

	      Control: Manual

	      Initial State: Shop owner with existing account and not logged in

	      Input: Shop owner submits login form with valid email and password

	      Output: Redirect to shop owner landing page upon successful login

	      Test Case Derivation: Shop owner wants to login to existing with valid login credentials provided

	      How test will be performed: The tester will login to an existing shop owner account using valid
	      login credentials

	\item \textbf{FRT-BE2-3}

	      Control: Manual

	      Initial State: Employee with existing account and not logged in

	      Input: Employee submits login form with valid email and password

	      Output: Redirect to employee landing page upon successful login

	      Test Case Derivation: Employee wants to login to existing with valid login credentials provided

	      How test will be performed: The tester will login to an existing employee account using valid login
	      credentials

	\item \textbf{FRT-BE3-1}

	      Control: Manual

	      Initial State: Customer with existing account and not logged in

	      Input: Customer requests a password reset code to be sent to inputted email

	      Output: System sends password reset code to inputted email and displays a countdown for password
	      reset expiration

	      Test Case Derivation: Customer wants to reset password

	      How test will be performed: The tester will request a password reset with an email associated with
	      an existing account

	\item \textbf{FRT-BE3-2}

	      Control: Manual

	      Initial State: Shop owner with existing account and not logged in

	      Input: Shop owner requests a password reset code to be sent to inputted email

	      Output: System sends password reset code to inputted email and displays a countdown for password
	      reset expiration

	      Test Case Derivation: Shop owner wants to reset password

	      How test will be performed: The tester will request a password reset with an email associated with
	      an existing account

	\item \textbf{FRT-BE3-3}

	      Control: Manual

	      Initial State: Employee with existing account and not logged in

	      Input: Employee requests a password reset code to be sent to inputted email

	      Output: System sends password reset code to inputted email and displays a countdown for password
	      reset expiration

	      Test Case Derivation: Employee wants to reset password

	      How test will be performed: The tester will request a password reset with an email associated with
	      an existing account

\end{enumerate}

\subsubsection{Appointments}

This section will contain tests covering the ``Appointments'' requirements defined in the
\href{https://github.com/arkinmodi/project-sayyara/blob/main/docs/SRS/SRS.pdf}{SRS}.

\begin{enumerate}

	\item \textbf{FRT-BE4-1}

	      Control: Manual

	      Initial State: Customer account which received a quote from an auto shop

	      Input: Enters service request information and selects an available appointment time slot

	      Output: A new appointment request is created with service details linked to the quote. Shop
	      Owner/Employee Accounts will receive the appointment request

	      Test Case Derivation: The appointment will be requested with the details the user entered

	      How test will be performed: The tester will go through the appointment booking process through the
	      user interface through quotes

	\item \textbf{FRT-BE4-2}

	      Control: Manual

	      Initial State: Customer account selects a canned job at an auto shop

	      Input: Enters service request information and selects an available appointment time slot

	      Output: A new appointment request is created with service details. Shop Owner/Employee Accounts
	      will receive the appointment request

	      Test Case Derivation: The appointment will be requested with the canned job details as well as
	      details the user entered

	      How test will be performed: The tester will go through the appointment booking process through the
	      user interface by selecting a canned job

	\item \textbf{FRT-BE4-3}

	      Control: Manual

	      Initial State: Shop Owner/Employee Account with appointment to be scheduled

	      Input: Enters customer information, service request information and selects an available
	      appointment time slot

	      Output: A new appointment request is created with service details

	      Test Case Derivation: The appointment will be requested with the details the user entered

	      How test will be performed: The tester will go through the appointment booking process through the
	      user interface

	\item \textbf{FRT-BE4-4}

	      Control: Manual

	      Initial State: Shop Owner/Employee Account with appointment requests

	      Input: Accept an appointment request

	      Output: Appointment booking displayed in calendar for Shop Owner/Employee accounts and Customer
	      account

	      Test Case Derivation: The appointment request is accepted and appointment booking is completed

	      How test will be performed: The tester will accept an appointment request through the user
	      interface

	\item \textbf{FRT-BE5-1}

	      Control: Manual

	      Initial State: Customer Account has a service appointment scheduled

	      Input: Selects an appointment to edit and selects a new available time slot for the appointment

	      Output: A new appointment request is made with the new time slot. Shop Owner/Employee Accounts will
	      receive the appointment request

	      Test Case Derivation: The user is able to change their appointment to any of the available time
	      slots displayed

	      How test will be performed: The tester will go through the user interface to edit an appointment
	      booking

	\item \textbf{FRT-BE5-2}

	      Control: Manual

	      Initial State: Shop Owner/Employee Account has a service appointment scheduled

	      Input: Selects an appointment to edit and selects a new available time slot for the appointment

	      Output: The appointment booking is updated to the new time slot

	      Test Case Derivation: The user is able to change their appointment to any of the available time
	      slots displayed

	      How test will be performed: The tester will go through the user interface to edit an appointment
	      booking time slot

	\item \textbf{FRT-BE5-3}

	      Control: Manual

	      Initial State: Shop Owner/Employee Account has a service appointment scheduled

	      Input: Selects an appointment to edit service details

	      Output: The appointment booking is updated with the updated service details

	      Test Case Derivation: The user is able to update the appointment details

	      How test will be performed: The tester will go through the user interface to edit appointment
	      details

	\item \textbf{FRT-BE6-1}

	      Control: Manual

	      Initial State: Customer Account has a service appointment scheduled

	      Input: Selects an appointment to cancel

	      Output: The appointment booking is cancelled and removed from the customer and shop owner/employee
	      schedules

	      Test Case Derivation: The appointment should be removed from the calendar when it is cancelled

	      How test will be performed: The tester will go through the user interface to cancel an appointment

	\item \textbf{FRT-BE6-2}

	      Control: Manual

	      Initial State: Shop Owner/Shop Employee has a service appointment scheduled

	      Input: Selects an appointment to cancel

	      Output: The appointment booking is cancelled and removed from the customer and shop owner/employee
	      schedules

	      Test Case Derivation: The appointment should be removed from the calendar when it is cancelled

	      How test will be performed: The tester will go through the user interface to cancel an appointment

	\item \textbf{FRT-BE7-1}

	      Control: Manual

	      Initial State: Shop Owner selects appointment availability

	      Input: Sets appointment availabilities

	      Output: The appointment availability is updated in the database

	      Test Case Derivation: The appointment availability will be saved and availability time slots to
	      book appointments will be updated

	      How test will be performed: The tester will go through the user interface to set appointment
	      availabilities
\end{enumerate}

\subsubsection{Quotes}

This section will contain tests covering the ``Quotes'' requirements defined in the
\href{https://github.com/arkinmodi/project-sayyara/blob/main/docs/SRS/SRS.pdf}{SRS}.

\begin{enumerate}
	\item \textbf{FRT-BE8-1}

	      Control: Manual

	      Initial State: Customer Account with no quote requests initiated from the account

	      Input: Request past quotes

	      Output: A message saying there are no past quotes

	      Test Case Derivation: There are no past quotes to display

	      How test will be performed: The tester will request for past quotes through the user interface

	\item \textbf{FRT-BE8-2}

	      Control: Manual

	      Initial State: Customer Account with quotes requests which have been closed and were initiated by
	      the account

	      Input: Request past quotes

	      Output: A table with all the quotes

	      Test Case Derivation: There are past quotes to display

	      How test will be performed: The tester will request for past quotes through the user interface

	\item \textbf{FRT-BE8-3}

	      Control: Manual

	      Initial State: Shop Owner/Employee Account with no quotes requests assigned to the shop

	      Input: Request past quotes with quote ID, customer phone number, and/or customer name

	      Output: A message saying there are no past quotes

	      Test Case Derivation: There are no past quotes to display matching the inputted criteria

	      How test will be performed: The tester will request for past quotes through the user interface

	\item \textbf{FRT-BE8-4}

	      Control: Manual

	      Initial State: Shop Owner/Employee Account with closed quotes requests that were assigned to the
	      shop

	      Input: Request past quotes with quote ID, customer phone number, and/or customer name

	      Output: A table with all the quotes

	      Test Case Derivation: There are past quotes to display matching the inputted criteria

	      How test will be performed: The tester will request for past quotes through the user interface

	\item \textbf{FRT-BE9-1}

	      Control: Manual

	      Initial State: Customer Account with quotes requests which have been closed and were initiated by
	      the account

	      Input: Request quote details

	      Output: The quote details

	      Test Case Derivation: Display the quote details requested

	      How test will be performed: The tester will request for quote details through the user interface

	\item \textbf{FRT-BE9-2}

	      Control: Manual

	      Initial State: Shop Owner/Employee Account with closed quotes requests that were assigned to the
	      shop

	      Input: Request quote details

	      Output: The quote details

	      Test Case Derivation: Display the quote details requested

	      How test will be performed: The tester will request for quote details through the user interface

	\item \textbf{FRT-BE10-1}

	      Control: Manual

	      Initial State: Customer Account

	      Input: A filled in quote request form

	      Output: A confirmation messaging indicating that the quote was requested

	      Test Case Derivation: The system shall verify that the quote was created successfully

	      How test will be performed: The tester will create a quote through the user interface

	\item \textbf{FRT-BE10-2}

	      Control: Manual

	      Initial State: Shop Owner/Employee Account with a registered shop

	      Input: A quote is requested from the shop

	      Output: A notification for the open quote request

	      Test Case Derivation: The system shall notify that a quote was created

	      How test will be performed: The tester will create a quote through the user interface

	\item \textbf{FRT-BE11-1}

	      Control: Manual

	      Initial State: Customer Account with a created quote

	      Input: Request to delete quote with the quote's ID

	      Output: A quote deleted confirmation message

	      Test Case Derivation: The system shall delete the quote upon request

	      How test will be performed: The tester will delete a quote through the user interface

	\item \textbf{FRT-BE12-1}

	      Control: Manual

	      Initial State: Customer Account with a created quote

	      Input: Request to update quote with the quote's new details

	      Output: A quote updated confirmation message

	      Test Case Derivation: The system shall update the quote upon request

	      How test will be performed: The tester will update a quote through the user interface

	\item \textbf{FRT-BE12-2}

	      Control: Manual

	      Initial State: Shop Owner/Employee Account with a registered shop and an active quote

	      Input: A quote's details are updated

	      Output: A notification for the updated quote

	      Test Case Derivation: The system shall notify that a quote was updated

	      How test will be performed: The tester will update a quote through the user interface

	\item \textbf{FRT-BE13-1}

	      Control: Manual

	      Initial State: Customer Account with a created quote

	      Input: A request to create a new quote using details from another quote which is identified by
	      quote ID

	      Output: A confirmation messaging indicating that the quote was requested

	      Test Case Derivation: The system shall verify that the quote was created successfully with an
	      existing quote's details

	      How test will be performed: The tester will create a quote through the user interface

	\item \textbf{FRT-BE14-1}

	      Control: Manual

	      Initial State: Customer Account with a created quote

	      Input: A response to a quote

	      Output: A notification for the responded to quote

	      Test Case Derivation: The system shall notify that a quote was responded to

	      How test will be performed: The tester will create a response to a quote through the user interface

	\item \textbf{FRT-BE14-2}

	      Control: Manual

	      Initial State: Shop Owner/Employee Account with a registered shop and an active quote

	      Input: A response to a quote

	      Output: A quote responded confirmation message

	      Test Case Derivation: The system shall verify that the quote was responded to successfully

	      How test will be performed: The tester will create a response to a quote through the user interface

	\item \textbf{FRT-BE15-1}

	      Control: Manual

	      Initial State: Customer Account with a responded to quote

	      Input: Accept a responded to quote

	      Output: The system shall request the user to create an appointment with the shop that responded

	      Test Case Derivation: The system shall have the user create an appointment upon accepting a quote

	      How test will be performed: The tester will accept a quote through the user interface

	\item \textbf{FRT-BE16-1}

	      Control: Manual

	      Initial State: Customer Account with a created quote

	      Input: A message to request additional information

	      Output: A message sent confirmation

	      Test Case Derivation: The system shall confirm to the user that the message was sent

	      How test will be performed: The tester will send a message for additional information through the
	      user interface

	\item \textbf{FRT-BE16-2}

	      Control: Manual

	      Initial State: Shop Owner/Employee Account with a registered shop and an active quote

	      Input: A message to request additional information

	      Output: A message sent confirmation

	      Test Case Derivation: The system shall confirm to the user that the message was sent

	      How test will be performed: The tester will send a message for additional information through the
	      user interface
\end{enumerate}

\subsubsection{Work Orders}

This section will contain tests covering the ``Work Orders'' requirements defined in the
\href{https://github.com/arkinmodi/project-sayyara/blob/main/docs/SRS/SRS.pdf}{SRS}.

\begin{enumerate}

	\item \textbf{FRT-BE17-1}

	      Control: Manual

	      Initial State: Shop Owner/Employee Account with a registered shop and a quote

	      Input: A new appointment created at the shop from the quote

	      Output: A new work order is created with details from the quote

	      Test Case Derivation: The system shall automatically create a work order for new appointment with
	      information from the quote

	      How test will be performed: The tester will create an appointment through the user interface

	\item \textbf{FRT-BE17-2}

	      Control: Manual

	      Initial State: Shop Owner/Employee Account with a registered shop

	      Input: A new appointment created at the shop

	      Output: A new work order is created

	      Test Case Derivation: The system shall automatically create a work order for new appointment

	      How test will be performed: The tester will create an appointment through the user interface

	\item \textbf{FRT-BE18-1}

	      Control: Manual

	      Initial State: Shop Owner/Employee Account with a registered shop, an upcoming appointment, and a
	      work order associated to the appointment

	      Input: Appointment is deleted

	      Output: Appointment and Work Order deleted confirmation message

	      Test Case Derivation: The system shall delete appointment and the associated work order upon
	      request

	      How test will be performed: The tester will delete an appointment through the user interface

	\item \textbf{FRT-BE19-1}

	      Control: Manual

	      Initial State: Shop Owner/Employee Account with a registered shop, an upcoming appointment, and a
	      work order associated to the appointment

	      Input: Work Order is searched by the customer name, assigned employee, service type, and/or a date
	      range

	      Output: The work orders matching the inputted criteria in a table format

	      Test Case Derivation: The system shall display work order upon request

	      How test will be performed: The tester will search for a work order through the user interface

	\item \textbf{FRT-BE20-1}

	      Control: Manual

	      Initial State: Shop Owner/Employee Account with a registered shop, an upcoming appointment, and a
	      work order associated to the appointment

	      Input: Request to view past work orders

	      Output: Past work orders in a table format

	      Test Case Derivation: The system shall display work order upon request

	      How test will be performed: The tester will search for past work orders through the user interface

	\item \textbf{FRT-BE21-1}

	      Control: Manual

	      Initial State: Shop Owner/Employee Account with a registered shop, an upcoming appointment, and a
	      work order associated to the appointment

	      Input: Request to update a work order with new details

	      Output: A work order updated confirmation message

	      Test Case Derivation: The system shall update work order upon request

	      How test will be performed: The tester will update a work order through the user interface

	\item \textbf{FRT-BE22-1}

	      Control: Manual

	      Initial State: Shop Owner/Employee Account with a registered shop, an appointment, and a work order
	      associated to the appointment

	      Input: A customer has paid for their appointment

	      Output: The work order is emailed to the customer, and the appointment and work order are marked as
	      ``completed''

	      Test Case Derivation: The system shall mark work orders and appointments as completed when the
	      customer has paid for the word done

	      How test will be performed: The tester will mark a work order as completed through the user
	      interface

	\item \textbf{FRT-BE23-1}

	      Control: Manual

	      Initial State: Shop Owner/Employee Account with a registered shop, an appointment, and a work order
	      associated to the appointment

	      Input: Request work order details

	      Output: The work order details

	      Test Case Derivation: The system shall display work orders details upon request

	      How test will be performed: The tester will view a work order's details through the user interface

\end{enumerate}

\subsubsection{Employee Management}

This section will contain tests covering the ``Employee Management'' requirements defined in the
\href{https://github.com/arkinmodi/project-sayyara/blob/main/docs/SRS/SRS.pdf}{SRS}.

\begin{enumerate}

	\item \textbf{FRT-BE24-1}

	      Control: Manual

	      Initial State: Shop owner account with no employees invited to shop yet

	      Input: Shop owner enters a list of employee emails to invite

	      Output: System sends invitation to employee emails provided

	      Test Case Derivation: The system shall allow the user to enter employee email(s) to invite; the
	      system shall send an invitation email to the invited employee(s)

	      How test will be performed: The tester will use a shop owner account to send employee invitation
	      emails

	\item \textbf{FRT-BE24-2}

	      Control: Manual

	      Initial State: Employee account with invitation email

	      Input: Employee uses invitation email to sign up

	      Output: System displays employee sign up form

	      Test Case Derivation: The system shall allow the user to accept an invitation

	      How test will be performed: The tester will attempt to accept an employee invitation email

	\item \textbf{FRT-BE25-1}

	      Control: Manual

	      Initial State: Shop owner account with employees listed under the shop

	      Input: The user enters search text to search for an employee

	      Output: System displays a list of employees whose name or email matches the search text

	      Test Case Derivation: The system shall allow the user to enter search text to search for an
	      employee; the system shall display a list of employees whose name or email matches the search text

	      How test will be performed: The tester will use a shop owner account with employees listed under
	      the shop and enter search text to search for an employee

	\item \textbf{FRT-BE26-1}

	      Control: Manual

	      Initial State: Shop owner account with no employees

	      Input: The user attempts to view the list of employees

	      Output: Message indicating that there are currently no employees

	      Test Case Derivation: The shop owner with no employees wants to view the list of employees

	      How test will be performed: The tester will use a shop owner account with no employees listed under
	      the shop and attempt to view the list of employees

	\item \textbf{FRT-BE26-2}

	      Control: Manual

	      Initial State: Shop owner account with employees

	      Input: The user attempts to view the list of employees

	      Output: Table of employees details and employee management options

	      Test Case Derivation: The shop owner with employees wants to view the list of employees

	      How test will be performed: The tester will use a shop owner account with employees listed under
	      the shop and attempt to view the list of employees

	\item \textbf{FRT-BE27-1}

	      Control: Manual

	      Initial State: Shop owner account with employees

	      Input: The user attempts to remove an employee

	      Output: Table of employees details and employee management options updates with employee removed;
	      the remove employee's access should be revoked

	      Test Case Derivation: The shop owner with employees wants to remove an employee

	      How test will be performed: The tester will use a shop owner account with employees listed under
	      the shop and attempt to remove an employee

\end{enumerate}

\subsubsection{Services}

This section will contains tests covering the ``Services'' requirements defined in the
\href{https://github.com/arkinmodi/project-sayyara/blob/main/docs/SRS/SRS.pdf}{SRS}.

\begin{enumerate}

	\item \textbf{FRT-BE28-1}

	      Control: Manual

	      Initial State: Shop Owner has a shop profile

	      Input: Shop Owner adds available services

	      Output: Shop services are sent to the database and displayed on the shop profile

	      Test Case Derivation: The user can add available auto shop services to their shop profile

	      How test will be performed: The tester will add a service to the shop profile and confirms it shows
	      on the shop profile

	\item \textbf{FRT-BE29-1}

	      Control: Manual

	      Initial State: Active Customer Account

	      Input: Enters specific auto service in the search bar

	      Output: Auto shops with relevant services displayed with service details

	      Test Case Derivation: Services and auto shops relevant to the search query will be displayed

	      How test will be performed: The tester will search for shop services through the user interface and
	      confirms that the appropriate results are displayed

	\item \textbf{FRT-BE29-2}

	      Control: Manual

	      Initial State: Shop Owner/Shop Employee searches for auto repair or maintenance services

	      Input: Enters specific auto service in the search bar

	      Output: Auto shops with relevant services displayed with service details

	      Test Case Derivation: Services corresponding to the auto shop will be displayed

	      How test will be performed: The tester will search for shop services through the user interface and
	      confirms that all of the shop's services are listed

	\item \textbf{FRT-BE30-1}

	      Control: Manual

	      Initial State: Shop Owner with services listed on their shop profile

	      Input: Updates the details of a service listed on their profile

	      Output: The service is updated with the entered details

	      Test Case Derivation: The shop profile will list the service with the updated details

	      How test will be performed: The tester will update the details of a shop service through the user
	      interface and confirms that the shop profile is updated

	\item \textbf{FRT-BE31-1}

	      Control: Manual

	      Initial State: Shop Owner with services listed on their shop profile

	      Input: Deletes a service listed on their shop profile

	      Output: Service is removed from the shop profile. Other services that were not deleted continue to
	      be listed on the shop profile

	      Test Case Derivation: The service that is deleted is removed from the shop profile

	      How test will be performed: The tester will delete a shop service through the user interface and
	      confirms that the shop profile is updated

\end{enumerate}

\subsubsection{Shop Lookup}

This section will contain tests covering the ``Shop Lookup'' requirements defined in the
\href{https://github.com/arkinmodi/project-sayyara/blob/main/docs/SRS/SRS.pdf}{SRS}.

\begin{enumerate}
	\item \textbf{FRT-BE32-1}

	      Control: Manual

	      Initial State: Shop Owner/Employee Account with a registered shop, Customer Account exists

	      Input: The Customer Account attempts to view a list of shops, using the parameters of distance,
	      postal code, and/or shop name

	      Output: An output list of shops based on the input parameters

	      Test Case Derivation: The system shall show a list of shops with the specified parameters provided

	      How test will be performed: The tester will search for shops, and input various parameters to see
	      if the shop list changes correctly
\end{enumerate}

\subsubsection{Shop Profile}

This section will contain tests covering the ``Shop Profile'' requirements defined in the
\href{https://github.com/arkinmodi/project-sayyara/blob/main/docs/SRS/SRS.pdf}{SRS}.

\begin{enumerate}
	\item \textbf{FRT-BE33-1}

	      Control: Manual

	      Initial State: Shop Owner/Employee Account with a registered shop

	      Input: Request to view shop profile

	      Output: Information regarding the shop, which includes the shop's address, phone number, and email

	      Test Case Derivation: The system shall display information about the shop upon request

	      How test will be performed: The tester will go through the user interface to view a shop profile

	\item \textbf{FRT-BE34-1}

	      Control: Manual

	      Initial State: Shop Owner Account with a registered shop

	      Input: Request to update shop profile, with information which includes the shop's address, phone
	      number, and email

	      Output: A shop profile update confirmation message, and updated shop details

	      Test Case Derivation: The system shall update a shop's information upon request

	      How test will be performed: The tester will go through the user interface to update a shop profile,
	      on a Shop Owner Account

	\item \textbf{FRT-BE34-2}

	      Control: Manual

	      Initial State: Employee Account with a registered shop

	      Input: Request to update shop profile

	      Output: An error message regarding incorrect privilege

	      Test Case Derivation: The system shall not let employees update the shop profile

	      How test will be performed: The tester will attempt to update a shop profile on an Employee Account
\end{enumerate}

\subsubsection{Employee Profile}

This section will contain tests covering the ``Employee Profile'' requirements defined in the
\href{https://github.com/arkinmodi/project-sayyara/blob/main/docs/SRS/SRS.pdf}{SRS}.

\begin{enumerate}
	\item \textbf{FRT-BE35-1}

	      Control: Manual

	      Initial State: Shop Owner account with employees listed on their shop profile, Employee account
	      exists

	      Input: An Employee account views their employee profile

	      Output: Displays the employee's name, phone number and email

	      Test Case Derivation: The system shall display the employee's profile when requested

	      How test will be performed: The tester will navigate the interface to view their own profile

	\item \textbf{FRT-BE35-2}

	      Control: Manual

	      Initial State: Shop Owner account with employees listed on their shop profile, multiple Employee
	      accounts exist

	      Input: An Employee account views another employee's profile

	      Output: Does not display the information

	      Test Case Derivation: The system shall not display other employee's profiles

	      How test will be performed: The tester will navigate the interface to view another employee's
	      profile

	\item \textbf{FRT-BE35-3}

	      Control: Manual

	      Initial State: Shop Owner account with employees listed on their shop profile, Employee accounts
	      exist

	      Input: A Shop Owner account views an employee profile

	      Output: Displays the employee's name, phone number and email

	      Test Case Derivation: The system shall display the employee's profile to a Shop Owner when
	      requested

	      How test will be performed: The tester will navigate the interface to view many different employee
	      profiles

	\item \textbf{FRT-BE36-1}

	      Control: Manual

	      Initial State: Shop Owner account with employees listed on their shop profile, Employee account
	      exists

	      Input: An Employee account attempts to edit their own profile, by providing an email and/or a phone
	      number

	      Output: A notification of a successful update and their profile is updated accordingly

	      Test Case Derivation: The system shall allow the Employee account to edit their own profile

	      How test will be performed: The tester will edit their own profile by updating the email and phone
	      number fields

	\item \textbf{FRT-BE36-2}

	      Control: Manual

	      Initial State: Shop Owner account with employees listed on their shop profile, multiple Employee
	      accounts exist

	      Input: An Employee account attempts to update another employee's profile

	      Output: Nothing happens

	      Test Case Derivation: The system shall not allow Employee accounts to edit other employee profiles

	      How test will be performed: The tester will attempt to edit another employee's profile

	\item \textbf{FRT-BE36-3}

	      Control: Manual

	      Initial State: Shop Owner account with employees listed on their shop profile, Employee account
	      exists

	      Input: A Shop Owner account attempts to update any employee profile, providing an email and/or
	      phone number

	      Output: A notification of a successful update and the profile is updated accordingly

	      Test Case Derivation: The system shall allow Shop Owner accounts to update employee profiles

	      How test will be performed: The tester will attempt to edit multiple employee profiles

\end{enumerate}

\subsection{Tests for Nonfunctional Requirements}

% \wss{The nonfunctional requirements for accuracy will likely just reference the
% 	appropriate functional tests from above.  The test cases should mention
% 	reporting the relative error for these tests.  Not all projects will
% 	necessarily have nonfunctional requirements related to accuracy}

% \wss{Tests related to usability could include conducting a usability test and
% 	survey.  The survey will be in the Appendix.}

% \wss{Static tests, review, inspections, and walkthroughs, will not follow the
% 	format for the tests given below.}

\subsubsection{Look and Feel Requirements}

\begin{enumerate}

	\item \textbf{NFRT-LF1-1} % For LF1

	      Type: Dynamic, Manual

	      Initial State: The application is accessible through the Google Chrome web browser

	      Input/Condition: The window size is changed

	      Output/Result: The application shall adjust and scale to fit the new window size

	      How test will be performed: The tester will access the application through Google Chrome on their
	      desktop/laptop and change the windows through the use of Google Chrome DevTools Device Toolbar

	\item \textbf{NFRT-LF2-1} % For LF2

	      Type: Dynamic, Manual

	      Initial State: The application is accessible through the Google Chrome web browser

	      Input: The application is opened in a full screened web browser window

	      Output: All text on the screen shall be readable

	      How test will be performed: The tester open the application in a full screened web browser window,
	      navigate to all pages, and judge if all text on the screen is readable from sitting 50 centimeters
	      away from the monitor

	\item \textbf{NFRT-LF3-1} % For LF3

	      Type: Dynamic, Manual

	      Initial State: The application is accessible through the Google Chrome web browser and there is a
	      completed work order and quote on the user's account

	      Input: The user opens the work order details and the quote details

	      Output: All currency shall be rounded to two decimal places

	      How test will be performed: The tester will navigate to the work order and quote and verify that
	      all values of currency are rounded to two decimal places

\end{enumerate}

\subsubsection{Usability and Humanity Requirements}
\begin{enumerate}

	\item \textbf{NFRT-UH1-1} % For UH1

	      Type: Dynamic, Manual

	      How test will be performed: The testers will complete the manual system tests for functional
	      requirements listed section \ref{Tests for Functional Requirements} on a MacOS desktop/laptop
	      device, a Windows desktop/laptop, an iOS mobile device, and an android mobile device.

	\item \textbf{NFRT-UH2-1} % For UH2

	      Type: Dynamic, Manual

	      Initial State: Device is connected to the internet and application is not open

	      Input/Condition: The user launches the application on Google Chrome

	      Output/Result: The system can be assessed through Google Chrome

	      How test will be performed: The tester will attempt to launch the application on the Google Chrome
	      web browser and using a device that is connected to the internet.

	\item \textbf{NFRT-UH3-1} % For UH3

	      Type: Dynamic, Manual

	      Initial State: Device is connected to the internet and the application is open

	      Input/Condition: User disconnects from the internet

	      Output/Result: The system notifies the user that there is no network connection and functionality
	      will be limited.

	      How test will be performed: The tester disconnect from the internet while the application is open.

\end{enumerate}

\subsubsection{Performance Requirements}
\begin{enumerate}
	\item \textbf{NFRT-PR1-1} % For PR1

	      Type: Dynamic, Manual

	      How test will be performed: The tester will additionally add a timer to every test listed in
	      section \ref{Tests for Functional Requirements} to check if every user function responds within 0.5
	      seconds.

\end{enumerate}

\subsubsection{Operational and Environmental Requirements}
\begin{enumerate}

	\item \textbf{NFRT-OE1-1} % For OE1

	      Type: Dynamic, Manual

	      How test will be performed: The testers will complete the manual system tests for functional
	      requirements listed section \ref{Tests for Functional Requirements} on Google Chrome using various
	      device dimension options listed the Google DevTools Device Toolbar. At minimum, the testers will
	      test with the following dimensions: Responsive, iPhone 12 Pro ($390 \times 844$), iPhone SE ($375
		      \times 667$), and iPad Air ($820 \times 1180$). This set will provide a reasonable variety of
	      different device dimensions.

\end{enumerate}

\subsubsection{Maintainability and Support Requirements}
\begin{enumerate}
	\item \textbf{NFRT-MS1-1} % For MS1

	      Type: Manual

	      How test will be performed: Every document will have to pass a review by every developer before the
	      document is finalized. The review will include running through the system and linking every module
	      to proper documentation.

\end{enumerate}

\subsubsection{Security Requirements}
\begin{enumerate}

	\item \textbf{NFRT-SR1-1}

	      Type: Dynamic, Manual

	      Initial State: Two created accounts with both containing an appointment

	      Input/Condition: The user searches for an appointment ID not belonging to the account

	      Output/Result: An error message saying the appointment is not found

	      How test will be performed: The tester will search for the appointment by appointment ID through
	      the user interface

	\item \textbf{NFRT-SR1-2}

	      Type: Dynamic, Automatic

	      Initial State: An account with a created appointment

	      Input/Condition: An HTTP request to the application's backend to get the appointment by appointment
	      ID

	      Output/Result: The request is rejected with a 403 Forbidden error message

	      How test will be performed: Through Jest an HTTP request will be sent to the server

	\item \textbf{NFRT-SR2-1}

	      Type: Dynamic, Manual

	      Initial State: One Shop Owner account and two Customer accounts with one customer having an
	      appointment at the shop registered under the same Shop Owner account

	      Input/Condition: Request available time slots at the Shop Owner's store using both the Customer
	      without an appointment's account and the Shop Owner's account

	      Output/Result: The Customer should only be able to view the time slot taken by the other customer,
	      but the Shop Owner should be able to view all the information of the Customer that has taken the
	      time slot

	      How test will be performed: The tester will view the available time slots page as both the Customer
	      without an appointment and the Shop Owner

	\item \textbf{NFRT-SR2-2}

	      Type: Dynamic, Automatic

	      Initial State: One Shop Owner account and two Customer accounts with one customer having an
	      appointment at the shop registered under the same Shop Owner account

	      Input/Condition: An HTTP request to the application's backend to get the available time slots using
	      the Customer without an appointment's security token and again with the Shop Owner's security token

	      Output/Result: The Customer should only be able to view the time slot taken by the other customer,
	      but the Shop Owner should be able to view all the information of the Customer that has taken the
	      time slot

	      How test will be performed: Through Jest an HTTP request will be sent to the server as both the
	      Customer without an appointment and the Shop Owner

\end{enumerate}

\subsubsection{Cultural Requirements}
\begin{enumerate}
	\item \textbf{NFRT-CR1-1}

	      Type: Static, Manual

	      How test will be performed: The testers will go through end to end tests for the entire program and
	      will confirm that any texts or images are not offensive.

	\item \textbf{NFRT-CR2-1}

	      Type: Static, Manual

	      How test will be performed: The testers will go through end to end tests for the entire program and
	      will confirm that the text displayed is in English.

\end{enumerate}

\subsubsection{Legal Requirements}
\begin{enumerate}
	\item \textbf{NFRT-LR1-1}

	      Type: Static, Manual

	      How test will be performed: The testers will go through the source code of the project and project
	      documents to determine if any open source resources were used and check that appropriate credits
	      and/or copyright licenses are used.

\end{enumerate}

\newpage
\begin{landscape}
	\subsection{Traceability Between Test Cases and Requirements}

	\begin{longtable}{|l|cccccccccccccccc|}
		\caption{Traceability Between Functional Test Cases and Functional Requirements, BE1 to BE16}                                                                                                                                                                                                                           \\
		\hline
		\textbf{Test IDs}   & \multicolumn{16}{c|}{\textbf{Functional Requirement IDs}}                                                                                                                                                                                                                                         \\
		\hline
		~                   & \textbf{BE1}                                              & \textbf{BE2} & \textbf{BE3} & \textbf{BE4} & \textbf{BE5} & \textbf{BE6} & \textbf{BE7} & \textbf{BE8} & \textbf{BE9} & \textbf{BE10} & \textbf{BE11} & \textbf{BE12} & \textbf{BE13} & \textbf{BE14} & \textbf{BE15} & \textbf{BE16} \\
		\hline
		\textbf{FRT-BE1-1}  & X                                                         & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE1-2}  & X                                                         & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE1-3}  & X                                                         & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE2-1}  & ~                                                         & X            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE2-2}  & ~                                                         & X            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE2-3}  & ~                                                         & X            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE3-1}  & ~                                                         & ~            & X            & ~            & ~            & ~            & ~            & ~            & ~            & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE3-2}  & ~                                                         & ~            & X            & ~            & ~            & ~            & ~            & ~            & ~            & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE3-3}  & ~                                                         & ~            & X            & ~            & ~            & ~            & ~            & ~            & ~            & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE4-1}  & ~                                                         & ~            & ~            & X            & ~            & ~            & ~            & ~            & ~            & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE4-2}  & ~                                                         & ~            & ~            & X            & ~            & ~            & ~            & ~            & ~            & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE4-3}  & ~                                                         & ~            & ~            & X            & ~            & ~            & ~            & ~            & ~            & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE4-4}  & ~                                                         & ~            & ~            & X            & ~            & ~            & ~            & ~            & ~            & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE5-1}  & ~                                                         & ~            & ~            & ~            & X            & ~            & ~            & ~            & ~            & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE5-2}  & ~                                                         & ~            & ~            & ~            & X            & ~            & ~            & ~            & ~            & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE5-3}  & ~                                                         & ~            & ~            & ~            & X            & ~            & ~            & ~            & ~            & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE6-1}  & ~                                                         & ~            & ~            & ~            & ~            & X            & ~            & ~            & ~            & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE6-2}  & ~                                                         & ~            & ~            & ~            & ~            & X            & ~            & ~            & ~            & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE7-1}  & ~                                                         & ~            & ~            & ~            & ~            & ~            & X            & ~            & ~            & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE8-1}  & ~                                                         & ~            & ~            & ~            & ~            & ~            & ~            & X            & ~            & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE8-2}  & ~                                                         & ~            & ~            & ~            & ~            & ~            & ~            & X            & ~            & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE8-3}  & ~                                                         & ~            & ~            & ~            & ~            & ~            & ~            & X            & ~            & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE8-4}  & ~                                                         & ~            & ~            & ~            & ~            & ~            & ~            & X            & ~            & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE9-1}  & ~                                                         & ~            & ~            & ~            & ~            & ~            & ~            & ~            & X            & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE9-2}  & ~                                                         & ~            & ~            & ~            & ~            & ~            & ~            & ~            & X            & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE10-1} & ~                                                         & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & X             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE10-2} & ~                                                         & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & X             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE11-1} & ~                                                         & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~             & X             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE12-1} & ~                                                         & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~             & ~             & X             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE12-2} & ~                                                         & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~             & ~             & X             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE13-1} & ~                                                         & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~             & ~             & ~             & X             & ~             & ~             & ~             \\
		\textbf{FRT-BE14-1} & ~                                                         & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~             & ~             & ~             & ~             & X             & ~             & ~             \\
		\textbf{FRT-BE14-2} & ~                                                         & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~             & ~             & ~             & ~             & X             & ~             & ~             \\
		\textbf{FRT-BE15-1} & ~                                                         & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~             & ~             & ~             & ~             & ~             & X             & ~             \\
		\textbf{FRT-BE16-1} & ~                                                         & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~             & ~             & ~             & ~             & ~             & ~             & X             \\
		\textbf{FRT-BE16-2} & ~                                                         & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~             & ~             & ~             & ~             & ~             & ~             & X             \\
		\hline
	\end{longtable}

	\newpage

	\begin{longtable}{|l|ccccccccccccccc|}
		\caption{Traceability Between Functional Test Cases and Functional Requirements, BE17 to BE31}                                                                                                                                                                                                                  \\
		\hline
		\textbf{Test IDs}   & \multicolumn{15}{c|}{\textbf{Functional Requirement IDs}}                                                                                                                                                                                                                                 \\
		\hline
		~                   & \textbf{BE17}                                             & \textbf{BE18} & \textbf{BE19} & \textbf{BE20} & \textbf{BE21} & \textbf{BE21} & \textbf{BE23} & \textbf{BE24} & \textbf{BE25} & \textbf{BE26} & \textbf{BE27} & \textbf{BE28} & \textbf{BE29} & \textbf{BE30} & \textbf{BE31} \\
		\hline
		\textbf{FRT-BE17-1} & X                                                         & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE17-2} & X                                                         & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE18-1} & ~                                                         & X             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE19-1} & ~                                                         & ~             & X             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE20-1} & ~                                                         & ~             & ~             & X             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE21-1} & ~                                                         & ~             & ~             & ~             & X             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE22-1} & ~                                                         & ~             & ~             & ~             & ~             & X             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE23-1} & ~                                                         & ~             & ~             & ~             & ~             & ~             & X             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE24-1} & ~                                                         & ~             & ~             & ~             & ~             & ~             & ~             & X             & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE24-2} & ~                                                         & ~             & ~             & ~             & ~             & ~             & ~             & X             & ~             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE25-1} & ~                                                         & ~             & ~             & ~             & ~             & ~             & ~             & ~             & X             & ~             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE26-1} & ~                                                         & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & X             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE26-2} & ~                                                         & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & X             & ~             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE27-1} & ~                                                         & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & X             & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE28-1} & ~                                                         & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & X             & ~             & ~             & ~             \\
		\textbf{FRT-BE29-1} & ~                                                         & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & X             & ~             & ~             \\
		\textbf{FRT-BE29-2} & ~                                                         & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & X             & ~             & ~             \\
		\textbf{FRT-BE30-1} & ~                                                         & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & X             & ~             \\
		\textbf{FRT-BE31-1} & ~                                                         & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & ~             & X             \\
		\hline
	\end{longtable}

	\newpage

	\begin{longtable}{|l|ccccc|}
		\caption{Traceability Between Functional Test Cases and Functional Requirements, BE32 to BE36}                                                 \\
		\hline
		\textbf{Test IDs}   & \multicolumn{5}{c|}{\textbf{Functional Requirement IDs}}                                                                 \\
		\hline
		~                   & \textbf{BE32}                                            & \textbf{BE33} & \textbf{BE34} & \textbf{BE35} & \textbf{BE36} \\
		\hline
		\textbf{FRT-BE32-1} & X                                                        & ~             & ~             & ~             & ~             \\
		\textbf{FRT-BE33-1} & ~                                                        & X             & ~             & ~             & ~             \\
		\textbf{FRT-BE34-1} & ~                                                        & ~             & X             & ~             & ~             \\
		\textbf{FRT-BE34-2} & ~                                                        & ~             & X             & ~             & ~             \\
		\textbf{FRT-BE35-1} & ~                                                        & ~             & ~             & X             & ~             \\
		\textbf{FRT-BE35-2} & ~                                                        & ~             & ~             & X             & ~             \\
		\textbf{FRT-BE35-3} & ~                                                        & ~             & ~             & X             & ~             \\
		\textbf{FRT-BE36-1} & ~                                                        & ~             & ~             & ~             & X             \\
		\textbf{FRT-BE36-2} & ~                                                        & ~             & ~             & ~             & X             \\
		\textbf{FRT-BE36-3} & ~                                                        & ~             & ~             & ~             & X             \\
		\hline
	\end{longtable}

	\newpage

	\begin{longtable}{|l|cccccccccccccc|}
		\caption{Traceability Between Nonfunctional Test Cases and Nonfunctional Requirements}                                                                                                                                                                                             \\
		\hline
		\textbf{Test IDs}   & \multicolumn{14}{c|}{\textbf{Functional Requirement IDs}}                                                                                                                                                                                                    \\
		\hline
		~                   & \textbf{LF1}                                              & \textbf{LF2} & \textbf{LF3} & \textbf{UH1} & \textbf{UH2} & \textbf{UH3} & \textbf{PR1} & \textbf{OE1} & \textbf{MS1} & \textbf{SR1} & \textbf{SR2} & \textbf{CR1} & \textbf{CR2} & \textbf{LR1} \\
		\hline
		\textbf{NFRT-LF1-1} & X                                                         & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            \\
		\textbf{NFRT-LF2-1} & ~                                                         & X            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            \\
		\textbf{NFRT-LF3-1} & ~                                                         & ~            & X            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            \\
		\textbf{NFRT-UH1-1} & ~                                                         & ~            & ~            & X            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            \\
		\textbf{NFRT-UH2-1} & ~                                                         & ~            & ~            & ~            & X            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            \\
		\textbf{NFRT-UH3-1} & ~                                                         & ~            & ~            & ~            & ~            & X            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            \\
		\textbf{NFRT-PR1-1} & ~                                                         & ~            & ~            & ~            & ~            & ~            & X            & ~            & ~            & ~            & ~            & ~            & ~            & ~            \\
		\textbf{NFRT-OE1-1} & ~                                                         & ~            & ~            & ~            & ~            & ~            & ~            & X            & ~            & ~            & ~            & ~            & ~            & ~            \\
		\textbf{NFRT-MS1-1} & ~                                                         & ~            & ~            & ~            & ~            & ~            & ~            & ~            & X            & ~            & ~            & ~            & ~            & ~            \\
		\textbf{NFRT-SR1-1} & ~                                                         & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & X            & ~            & ~            & ~            & ~            \\
		\textbf{NFRT-SR1-2} & ~                                                         & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & X            & ~            & ~            & ~            & ~            \\
		\textbf{NFRT-SR2-1} & ~                                                         & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & X            & ~            & ~            & ~            \\
		\textbf{NFRT-SR2-2} & ~                                                         & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & X            & ~            & ~            & ~            \\
		\textbf{NFRT-CR1-1} & ~                                                         & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & X            & ~            & ~            \\
		\textbf{NFRT-CR2-1} & ~                                                         & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & X            & ~            \\
		\textbf{NFRT-LR1-1} & ~                                                         & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & ~            & X            \\
		\hline
	\end{longtable}
\end{landscape}

\section{Unit Test Description} \label{Unit Test Description}

\subsection{Unit Testing Scope}

% \wss{What modules are outside of the scope.  If there are modules that are
% 	developed by someone else, then you would say here if you aren't planning on
% 	verifying them.  There may also be modules that are part of your software, but
% 	have a lower priority for verification than others.  If this is the case,
% 	explain your rationale for the ranking of module importance.}

All modules defined in the Module Interface Specification are within the scope testing with
exception for the Database Driver Module. This module is largely composed of generated types and
logic from a third party library, Prisma. It assumed that Prisma's logic is correct and therefore
shall not be tested.

\subsection{Tests for Functional Requirements}

% \wss{Most of the verification will be through automated unit testing.  If
% 	appropriate specific modules can be verified by a non-testing based
% 	technique.  That can also be documented in this section.}

\subsubsection{Users Module}

% \wss{Include a blurb here to explain why the subsections below cover the module.
% References to the MIS would be good.  You will want tests from a black box
% perspective and from a white box perspective.  Explain to the reader how the
% tests were selected.}

This section will contain tests covering the ``Users Module'' defined in the
\href{https://github.com/arkinmodi/project-sayyara/blob/main/docs/Design/MIS/MIS.pdf}{MIS}. These
tests were chosen based on common user flows and internal execution patterns.

\begin{enumerate}

	\item \textbf{FRT-M3-1}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: N/A

	      Input: Create customer request received with valid information

	      Output: Customer and Vehicle are created

	      Test Case Derivation: New customer wants to sign up for a new account with valid sign up
	      information provided

	      How test will be performed: Jest will send the create customer request with valid information

	\item \textbf{FRT-M3-2}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: N/A

	      Input: Create customer request received with invalid information

	      Output: Request is rejected

	      Test Case Derivation: New customer wants to sign up for a new account but not all information is
	      provided

	      How test will be performed: Jest will send the create customer request with invalid information

	\item \textbf{FRT-M3-3}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: N/A

	      Input: Create shop owner request received with valid information

	      Output: Shop Owner and Shop are created

	      Test Case Derivation: New shop owner wants to sign up for a new account with valid sign up
	      information provided

	      How test will be performed: Jest will send the create shop owner request with valid information

	\item \textbf{FRT-M3-4}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: N/A

	      Input: Create shop owner request received with invalid information

	      Output: Request is rejected

	      Test Case Derivation: New shop owner wants to sign up for a new account but not all information is
	      provided

	      How test will be performed: Jest will send the create shop owner request with invalid information

	\item \textbf{FRT-M3-5}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: N/A

	      Input: Create employee request received with valid information

	      Output: Employee is created and register to given shop

	      Test Case Derivation: New employee wants to sign up for a new account with valid sign up
	      information provided

	      How test will be performed: Jest will send the create employee request with valid information

	\item \textbf{FRT-M3-6}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: N/A

	      Input: Create employee request received with invalid information

	      Output: Request is rejected

	      Test Case Derivation: New employee wants to sign up for a new account but not all information is
	      provided

	      How test will be performed: Jest will send the create employee request with invalid information

	\item \textbf{FRT-M3-7}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A user exists

	      Input: Get user by an email address for an existing user

	      Output: The user

	      Test Case Derivation: Need to look up user data by the user provided email address

	      How test will be performed: Jest will call the internal command to get a user by email address

	\item \textbf{FRT-M3-8}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A user exists

	      Input: Get user by an email address for a user that does not exist

	      Output: None

	      Test Case Derivation: Need to look up user data by the user provided email address

	      How test will be performed: Jest will call the internal command to get a user by email address

	\item \textbf{FRT-M3-9}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A user exists

	      Input: Authorize a user with a valid email and password

	      Output: The user's data

	      Test Case Derivation: A user wants to authorize themselves in order to view their data (e.g.,
	      appointments, work orders, etc.)

	      How test will be performed: Jest will call the internal command to authorize a user

	\item \textbf{FRT-M3-10}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A user exists

	      Input: Authorize a user with an invalid email and password

	      Output: A unauthorized error message

	      Test Case Derivation: A user wants to authorize themselves in order to view their data (e.g.,
	      appointments, work orders, etc.)

	      How test will be performed: Jest will call the internal command to authorize a user

\end{enumerate}

\subsubsection{Quotes Module}

This section will contain tests covering the ``Quotes Module'' defined in the
\href{https://github.com/arkinmodi/project-sayyara/blob/main/docs/Design/MIS/MIS.pdf}{MIS}. These
tests were chosen based on common user flows.

\begin{enumerate}

	\item \textbf{FRT-M4-1}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A customer, a vehicle, a shop, a shop owner, and a ``CUSTOM'' service exists

	      Input: Create quote request with valid information

	      Output: A quote is created

	      Test Case Derivation: A customer wants to request a quote from a shop

	      How test will be performed: Jest will send a create quote request with valid information

	\item \textbf{FRT-M4-2}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A customer, a vehicle, a shop, a shop owner, and a ``CUSTOM'' service exists

	      Input: Create quote request with invalid information

	      Output: Request is rejected

	      Test Case Derivation: A customer wants to request a quote from a shop

	      How test will be performed: Jest will send a create quote request with invalid information

	\item \textbf{FRT-M4-3}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A quote exists

	      Input: Update quote request with a valid ID and valid information

	      Output: The quote is updated

	      Test Case Derivation: A shop owner/employee wants to invite the customer to book an appointment and
	      need to prepopulate the booking with service information

	      How test will be performed: Jest will send an update quote request with a valid ID and valid
	      information

	\item \textbf{FRT-M4-4}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A quote exists

	      Input: Update quote request with an invalid ID and valid information

	      Output: Request is rejected

	      Test Case Derivation: A shop owner/employee wants to invite the customer to book an appointment and
	      need to prepopulate the booking with service information

	      How test will be performed: Jest will send an update quote request with an invalid ID and valid
	      information

	\item \textbf{FRT-M4-5}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A quote exists

	      Input: Update quote request with a valid ID and invalid information

	      Output: Request is rejected

	      Test Case Derivation: A shop owner/employee wants to invite the customer to book an appointment and
	      need to prepopulate the booking with service information

	      How test will be performed: Jest will send an update quote request with a valid ID and invalid
	      information

	\item \textbf{FRT-M4-6}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A quote exists

	      Input: Get quote request with a valid quote ID

	      Output: Quote data is returned

	      Test Case Derivation: A shop owner/employee wants to view the quote

	      How test will be performed: Jest will send a get quote request with a valid quote ID

	\item \textbf{FRT-M4-7}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A quote exists

	      Input: Get quote request with an invalid quote ID

	      Output: Request is rejected

	      Test Case Derivation: A shop owner/employee wants to view the quote

	      How test will be performed: Jest will send a get quote request with an invalid quote ID

	\item \textbf{FRT-M4-8}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A quote exists

	      Input: Get quote request with a valid customer ID

	      Output: List of quotes is returned

	      Test Case Derivation: A shop owner/employee wants to view the quote

	      How test will be performed: Jest will send a get quote request with a valid customer ID

	\item \textbf{FRT-M4-9}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A quote exists

	      Input: Get quote request with an invalid customer ID

	      Output: Empty list

	      Test Case Derivation: A shop owner/employee wants to view the quote

	      How test will be performed: Jest will send a get quote request with an invalid customer ID

	\item \textbf{FRT-M4-10}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A quote exists

	      Input: Get quote request with a valid shop ID

	      Output: List of quotes is returned

	      Test Case Derivation: A shop owner/employee wants to view the quote

	      How test will be performed: Jest will send a get quote request with a valid shop ID

	\item \textbf{FRT-M4-11}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A quote exists

	      Input: Get quote request with an invalid shop ID

	      Output: Empty list

	      Test Case Derivation: A shop owner/employee wants to view the quote

	      How test will be performed: Jest will send a get quote request with an invalid shop ID

	\item \textbf{FRT-M4-12}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A quote exists

	      Input: Delete quote request with a valid quote ID

	      Output: Quote and Chat Messages are deleted

	      Test Case Derivation: A user want to delete a quote and all associated chat messages

	      How test will be performed: Jest will send a delete quote request with a valid quote ID

	\item \textbf{FRT-M4-13}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A quote exists

	      Input: Delete quote request with an invalid quote ID

	      Output: No operation

	      Test Case Derivation: A shop owner/employee wants to view the quote

	      How test will be performed: Jest will send a delete quote request with an invalid quote ID

	\item \textbf{FRT-M4-14}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A quote exists

	      Input: Create a chat message request with valid information

	      Output: A chat message is created

	      Test Case Derivation: A user wants to send a chat message

	      How test will be performed: Jest will send a create chat message request with valid information

	\item \textbf{FRT-M4-15}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A quote exists

	      Input: Create a chat message request with invalid information

	      Output: Request is rejected

	      Test Case Derivation: A user wants to send a chat message

	      How test will be performed: Jest will send a create chat message request with invalid information

	\item \textbf{FRT-M4-16}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A quote exists

	      Input: Get chat messages request with a valid quote ID

	      Output: List of chat messages is returned

	      Test Case Derivation: A user want to see the previous chat messages

	      How test will be performed: Jest will send a get chat messages request with a valid quote ID

	\item \textbf{FRT-M4-17}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A quote exists

	      Input: Get chat messages request with an invalid quote ID

	      Output: Empty list

	      Test Case Derivation: A user want to see the previous chat messages

	      How test will be performed: Jest will send a get chat messages request with an invalid quote ID

\end{enumerate}

\subsubsection{Appointments Module}

This section will contain tests covering the ``Appointments Module'' defined in the
\href{https://github.com/arkinmodi/project-sayyara/blob/main/docs/Design/MIS/MIS.pdf}{MIS}. These
tests were chosen based on common user flows.

\begin{enumerate}

	\item \textbf{FRT-M5-1}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A customer, vehicle, shop, shop owner, and service exist

	      Input: Create appointment request with valid information

	      Output: An appointment and work order is created

	      Test Case Derivation: A customer wants to create an appointment at a shop

	      How test will be performed: Jest will send a create appointment request with valid information

	\item \textbf{FRT-M5-2}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A customer, vehicle, shop, shop owner, and service exist

	      Input: Create appointment request with missing information

	      Output: Request is rejected

	      Test Case Derivation: A customer wants to create an appointment at a shop

	      How test will be performed: Jest will send a create appointment request with missing information

	\item \textbf{FRT-M5-3}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A customer, vehicle, shop, shop owner, and service exist

	      Input: Create appointment request with an end time before the start time

	      Output: Request is rejected

	      Test Case Derivation: A customer wants to create an appointment at a shop

	      How test will be performed: Jest will send a create appointment request with invalid timing
	      information

	\item \textbf{FRT-M5-4}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: An appointment exists

	      Input: Get appointment request with a valid appointment ID

	      Output: Appointment data is returned

	      Test Case Derivation: A user wants to view an appointment

	      How test will be performed: Jest will send a get appointment request with a valid appointment ID

	\item \textbf{FRT-M5-5}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: An appointment exists

	      Input: Get appointment request with an invalid appointment ID

	      Output: Request is rejected

	      Test Case Derivation: A user wants to view an appointment

	      How test will be performed: Jest will send a get appointment request with an invalid appointment ID

	\item \textbf{FRT-M5-6}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: An appointment exists

	      Input: Get appointments request with a valid shop ID

	      Output: List of appointments is returned

	      Test Case Derivation: A shop owner/employee wants to view all appointments as their shop

	      How test will be performed: Jest will send a get appointments request with a valid shop ID

	\item \textbf{FRT-M5-7}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: An appointment exists

	      Input: Get appointments request with an invalid shop ID

	      Output: Empty list

	      Test Case Derivation: A shop owner/employee wants to view all appointments as their shop

	      How test will be performed: Jest will send a get appointments request with an invalid shop ID

	\item \textbf{FRT-M5-8}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: An appointment exists

	      Input: Update an appointment request with a valid appointment ID and valid information

	      Output: The appointment is updated

	      Test Case Derivation: A user wants to update the appointment

	      How test will be performed: Jest will send an update appointment request with a valid appointment
	      ID and valid information

	\item \textbf{FRT-M5-9}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: An appointment exists

	      Input: Update an appointment request with an invalid appointment ID and valid information

	      Output: Request is rejected

	      Test Case Derivation: A user wants to update the appointment

	      How test will be performed: Jest will send an update appointment request with an invalid
	      appointment ID and valid information

	\item \textbf{FRT-M5-10}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: An appointment exists

	      Input: Update an appointment request with a valid appointment ID and invalid information

	      Output: Request is rejected

	      Test Case Derivation: A user wants to update the appointment

	      How test will be performed: Jest will send an update appointment request with a valid appointment
	      ID and invalid information

	\item \textbf{FRT-M5-11}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: An appointment exists

	      Input: Update an appointment request with a valid appointment ID and with an end time before the
	      start time

	      Output: Request is rejected

	      Test Case Derivation: A user wants to update the appointment

	      How test will be performed: Jest will send an update appointment request with a valid appointment
	      ID and invalid timing information

	\item \textbf{FRT-M5-12}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: Multiple appointment exists with some having overlapping time slots

	      Input: Update an appointment request with a valid appointment ID and update status from
	      ``PENDING\_APPROVAL'' to ``ACCEPTED''

	      Output: The appointment is updated and all other overlapping appointment are updated to
	      ``REJECTED''

	      Test Case Derivation: A shop owner/employee wants to accept an appointment

	      How test will be performed: Jest will send an update appointment request with a valid appointment
	      ID and status as ``ACCEPTED''

	\item \textbf{FRT-M5-13}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: An appointment exists

	      Input: Delete appointment request with a valid appointment ID

	      Output: The appointment and work order should be deleted

	      Test Case Derivation: A user wants to delete an appointment

	      How test will be performed: Jest will send a delete appointment request with a valid appointment ID

	\item \textbf{FRT-M5-14}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: An appointment exists

	      Input: Delete appointment request with an invalid appointment ID

	      Output: No operation

	      Test Case Derivation: A user wants to delete an appointment

	      How test will be performed: Jest will send a delete appointment request with a valid appointment ID

\end{enumerate}

\subsubsection{Work Orders Module}

This section will contain tests covering the ``Work Orders Module'' defined in the
\href{https://github.com/arkinmodi/project-sayyara/blob/main/docs/Design/MIS/MIS.pdf}{MIS}. These
tests were chosen based on common user flows.

\begin{enumerate}

	\item \textbf{FRT-M6-1}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A work order exists

	      Input: Get work order request with a valid work order ID

	      Output: Work order data

	      Test Case Derivation: A user wants to view the work order

	      How test will be performed: Jest will send a get work order request with a valid work order ID

	\item \textbf{FRT-M6-2}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A work order exists

	      Input: Get work order request with an invalid work order ID

	      Output: Request is rejected

	      Test Case Derivation: A user wants to view the work order

	      How test will be performed: Jest will send a get work order request with an invalid work order ID

	\item \textbf{FRT-M6-3}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A work order exists

	      Input: Get work order request with a valid shop ID

	      Output: List of work orders

	      Test Case Derivation: A shop owner/employee wants to view all the work orders for their shop

	      How test will be performed: Jest will send a get work orders request with a valid shop ID

	\item \textbf{FRT-M6-4}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A work order exists

	      Input: Get work order request with an invalid shop ID

	      Output: Empty list

	      Test Case Derivation: A user wants to view the work order

	      How test will be performed: Jest will send a get work order request with an invalid shop ID

	\item \textbf{FRT-M6-5}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A work order exists

	      Input: Update work order request with a valid work order ID and valid information

	      Output: Update the work order

	      Test Case Derivation: A shop owner/employee wants to update the work order

	      How test will be performed: Jest will send an update work order request with a valid work order ID
	      and valid information

	\item \textbf{FRT-M6-6}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A work order exists

	      Input: Update work order request with an invalid work order ID and valid information

	      Output: Request is rejected

	      Test Case Derivation: A shop owner/employee wants to update the work order

	      How test will be performed: Jest will send an update work order request with an invalid work order
	      ID and valid information

	\item \textbf{FRT-M6-7}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A work order exists

	      Input: Update work order request with a valid work order ID and invalid information

	      Output: Request is rejected

	      Test Case Derivation: A shop owner/employee wants to update the work order

	      How test will be performed: Jest will send an update work order request with a valid work order ID
	      and invalid information

\end{enumerate}

\subsubsection{Employee Management Module}

\subsubsection{Services Module}

This section will contain tests covering the ``Services Module'' defined in the
\href{https://github.com/arkinmodi/project-sayyara/blob/main/docs/Design/MIS/MIS.pdf}{MIS}. These
tests were chosen based on common user flows.

\begin{enumerate}

	\item \textbf{FRT-M8-1}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A shop and a shop owner exist

	      Input: Create service request with valid information

	      Output: Create the service

	      Test Case Derivation: A shop owner wants to create a service at their shop

	      How test will be performed: Jest will send a create service request with valid information

	\item \textbf{FRT-M8-2}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A shop and a shop owner exist

	      Input: Create service request with invalid information

	      Output: Request is rejected

	      Test Case Derivation: A shop owner wants to create a service at their shop

	      How test will be performed: Jest will send a create service request with invalid information

	\item \textbf{FRT-M8-3}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A service exists

	      Input: Get service request with a valid service ID

	      Output: The service data

	      Test Case Derivation: A user wants to view a service

	      How test will be performed: Jest will send a get service request with a valid service ID

	\item \textbf{FRT-M8-4}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A service exists

	      Input: Get service request with an invalid service ID

	      Output: Request is rejected

	      Test Case Derivation: A user wants to view a service

	      How test will be performed: Jest will send a get service request with an invalid service ID

	\item \textbf{FRT-M8-5}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A service exists

	      Input: Get services request with a valid shop ID

	      Output: List of services

	      Test Case Derivation: A user wants to view the services at a shop

	      How test will be performed: Jest will send a get services request with a valid shop ID

	\item \textbf{FRT-M8-6}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A service exists

	      Input: Get services request with an invalid shop ID

	      Output: Request is rejected

	      Test Case Derivation: A user wants to view the services at a shop

	      How test will be performed: Jest will send a get services request with an invalid shop ID

	\item \textbf{FRT-M8-7}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A ``CANNED'' service exists

	      Input: Get ``CANNED'' services request with a valid shop ID

	      Output: List of ``CANNED'' services

	      Test Case Derivation: A user wants to view the ``CANNED'' services at a shop

	      How test will be performed: Jest will send a get ``CANNED'' services request with a valid shop ID

	\item \textbf{FRT-M8-8}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A ``CANNED'' service exists

	      Input: Get ``CANNED'' services request with an invalid shop ID

	      Output: Request is rejected

	      Test Case Derivation: A user wants to view the ``CANNED'' services at a shop

	      How test will be performed: Jest will send a get ``CANNED'' services request with an invalid shop
	      ID

	\item \textbf{FRT-M8-9}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A ``CUSTOM'' service exists

	      Input: Get ``CUSTOM'' services request with a valid shop ID

	      Output: List of ``CUSTOM'' services

	      Test Case Derivation: A user wants to view the ``CUSTOM'' services at a shop

	      How test will be performed: Jest will send a get ``CUSTOM'' services request with a valid shop ID

	\item \textbf{FRT-M8-10}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A ``CUSTOM'' service exists

	      Input: Get ``CUSTOM'' services request with an invalid shop ID

	      Output: Request is rejected

	      Test Case Derivation: A user wants to view the ``CUSTOM'' services at a shop

	      How test will be performed: Jest will send a get ``CUSTOM'' services request with an invalid shop
	      ID

	\item \textbf{FRT-M8-11}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A service exists

	      Input: Update a service request with a valid service ID and valid information

	      Output: The service is updated

	      Test Case Derivation: A shop owner wants to update the details of their service

	      How test will be performed: Jest will send an update service request with a valid service ID and
	      valid information

	\item \textbf{FRT-M8-12}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A service exists

	      Input: Update a service request with an invalid service ID and valid information

	      Output: Request is rejected

	      Test Case Derivation: A shop owner wants to update the details of their service

	      How test will be performed: Jest will send an update service request with an invalid service ID and
	      valid information

	\item \textbf{FRT-M8-13}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A service exists

	      Input: Update a service request with a valid service ID and invalid information

	      Output: Request is rejected

	      Test Case Derivation: A shop owner wants to update the details of their service

	      How test will be performed: Jest will send an update service request with a valid service ID and
	      invalid information

	\item \textbf{FRT-M8-14}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A service exists

	      Input: Delete a service request with a valid service ID

	      Output: The service is deleted

	      Test Case Derivation: A shop owner wants to delete their service

	      How test will be performed: Jest will send a delete service request with a valid service ID

	\item \textbf{FRT-M8-15}

	      Type: Functional, Dynamic, Unit, Automated

	      Initial State: A service exists

	      Input: Delete a service request with an invalid service ID

	      Output: No operation

	      Test Case Derivation: A shop owner wants to delete their service

	      How test will be performed: Jest will send a delete service request with an invalid service ID

\end{enumerate}

\subsubsection{Shop Module}

\subsection{Tests for Nonfunctional Requirements}

\wss{If there is a module that needs to be independently assessed for
	performance, those test cases can go here.  In some projects, planning for
	nonfunctional tests of units will not be that relevant.}

\wss{These tests may involve collecting performance data from previously
	mentioned functional tests.}

\subsubsection{Module ?}

\begin{enumerate}

	\item{test-id1\\}

	Type: \wss{Functional, Dynamic, Manual, Automatic, Static etc. Most will be automatic}

	Initial State:

	Input/Condition:

	Output/Result:

	How test will be performed:

	\item{test-id2\\}

	Type: Functional, Dynamic, Manual, Static etc.

	Initial State:

	Input:

	Output:

	How test will be performed:

\end{enumerate}

\subsubsection{Module ?}

...

\subsection{Traceability Between Test Cases and Modules}

\wss{Provide evidence that all of the modules have been considered.}

\bibliographystyle{plainnat}

\bibliography{../../refs/References}

\newpage

\section{Appendix}

% This is where you can place additional information.

% \subsection{Symbolic Parameters}

% The definition of the test cases will call for SYMBOLIC\_CONSTANTS. Their values are defined in
% this section for easy maintenance.

% \subsection{Usability Survey Questions?}

% \wss{This is a section that would be appropriate for some projects.}

\subsection{Reflection}

\textbf{The information in this section will be used to evaluate the team members on the graduate attribute
	of Lifelong Learning. Please answer the following questions:}

\begin{enumerate}
	\item \textbf{What knowledge and skills will the team collectively need to acquire to successfully complete the
		      verification and validation of your project? Examples of possible knowledge and skills include
		      dynamic testing knowledge, static testing knowledge, specific tool usage etc. You should look to
		      identify at least one item for each team member.}

	      The team members will need to collectively acquire a set of unique skills to successfully complete
	      the verification and validation of Sayyara. Some skills and knowledge outlined below are critical
	      not only for the delivery of the project milestones, but also in the ensuring the application is
	      delivered in a fully functional state that satisfies both the requirements and goals for this
	      system. These skills will also contribute to each individual team member's success moving forward
	      in their software engineering careers.

	      \begin{enumerate}[\arabic*.]
		      \item Domain knowledge and skills specific to testing of PWAs
		      \item Acquire knowledge and skills related to testing tools: Jest, React Testing Library
		      \item Gain an understanding of language specific typechecking (i.e., TypeScript)
		      \item Familiarize with Code Review process and best practices
		      \item Develop a better understanding of dynamic and static testing methods pertaining to testing a full
		            stack progressive web application
		      \item Acquire knowledge relating to best industry practices and methodologies for manual integration
		            testing of progressive web applications
	      \end{enumerate}

	\item \textbf{For each of the knowledge areas and skills identified in the previous question, what are at least
		      two approaches to acquiring the knowledge or mastering the skill? Of the identified approaches,
		      which will each team member pursue, and why did they make this choice?}

	      \textbf{Arkin Modi}

	      Chosen Skills: 1., 2., 3., 5.

	      All of Arkin's chosen skill pertain to domain knowledge and best practices. These chosen skills are
	      areas of passion for Arkin as he has a deep interesting in learning about best practices and how he
	      can improve his day-to-day development skills. For skills based on tools, Arkin will be relying on
	      YouTube tutorials and the tool specific documentation to fill in gaps in his knowledge. For the
	      skill relating to more abstract topics (e.g., testing best practices), he will be utilizing YouTube
	      videos and online articles discussing the many ways these topics can be approached. These methods
	      are what have work best for Arkin in the past, and he already has an understanding on where to look
	      for the missing information.

	      \textbf{Joy Xiao}

	      Chosen Skills: 1., 2.

	      Joy has chosen to learn the domain knowledge and skills for testing PWAs. Learning more about how
	      to test PWAs is essential to the project because it is one of the main features of our application.
	      This will be done by accessing various online resources by searching how to test PWAs and looking
	      through the documentation and any informational videos to learn how it works from end to end. Joy
	      will also acquire knowledge and skills related to testing tools such as Jest and the React Testing
	      library by looking through official documentation from these resources and supplementing by any
	      video demonstration resources when needed. By learning each of these areas, it would be very
	      beneficial for performing the testing of our project as well as skills for future career growth as
	      many of the concepts can be used for many different situations.

	      \textbf{Leon So}

	      Chosen Skills: 1., 2., 5., 6.

	      Leon has chosen to improve and develop skills related to the testing of PWAs. In specific, Leon
	      will need to acquire skills related to the testing tools and technologies used for this project.
	      This can be done by referring to online resources and documentation related to testing Progressive
	      Web Applications and the technologies used. To develop a better understanding of dynamic and static
	      testing methods pertaining to testing a full stack progressive web application, Leon will refer to
	      course and academic materials and fill any PWA specific gaps with research from online sources.
	      Similarly, for industry best practices and methodologies, Leon will seek guidance from official
	      documentation published by various industry companies, institutions, and sources with known
	      experience working with PWAs. Each of the above development areas will contribute to building a set
	      of knowledge, skills, and understanding that Leon can directly apply to his future work and career.
	      These identified knowledge and skill areas will also allow Leon to contribute effectively to the
	      overall success of the project.

	      \textbf{Timothy Choy}

	      Chosen Skills: 1., 2., 4., 6.

	      Timothy has chosen to pursue the skills stated in the list above. He made this choice because he
	      does not have a lot of expertise with testing PWAs as well as TypeScript in general, and would like
	      to add these testing skills and tools to his toolbox. Furthermore, he wants to gain knowledge of
	      how the industry tests, both through code reviews and manual testing, and would like to replicate
	      how it is done in a professional setting in this project. To approach acquiring these skills and
	      knowledge, Timothy will do research on PWA testing and the tools used for testing, such as Jest and
	      the React testing library. Research will be done through reading documentation and watching video
	      tutorials. To get a sense of how the industry performs code reviews and manual testing, Timothy
	      will reach out to project members who have had more experience in a professional setting (through
	      internships), as well as reach out to his coworkers at his past internship for ideas.

\end{enumerate}

\end{document}
