\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}

\title{Problem Statement and Goals\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

\begin{table}[hp]
	\caption{Revision History} \label{TblRevisionHistory}
	\begin{tabularx}{\textwidth}{llX}
		\toprule
		\textbf{Date}      & \textbf{Developer(s)} & \textbf{Change}                           \\
		\midrule
		September 20, 2022 & Joy Xiao              & Problem statement and stakeholders        \\
		September 23, 2022 & Leon So               & Update problem                            \\
		September 23, 2022 & Joy Xiao              & Add stretch goals and update stakeholders \\
		September 23, 2022 & Leon So               & Add inputs and outputs                    \\
		September 25, 2022 & Leon So               & Add hardware and software environment     \\
		September 25, 2022 & Joy Xiao              & Add project goals                         \\
		September 25, 2022 & Leon So               & Add problem statement section outline     \\
		September 26, 2022 & Leon So               & Update inputs, outputs, goals             \\
		March 14, 2023     & Joy Xiao              & Update problem                            \\
		\bottomrule
	\end{tabularx}
\end{table}

\section{Problem Statement}
This section outlines the problem, inputs and outputs, stakeholders, and environment.

\subsection{Problem}
Independent auto repair shops do not have an efficient way of reaching and interacting with new
customers. Currently, many independent shop owners rely on word-of-mouth referrals as a main
channel to acquiring new customers. Independent auto repair shops are also spending a significant
amount of their time on administrative work such as managing appointments and providing quotes. As
a result, independent auto repair shops have a difficult time competing with larger repair shops
which have dedicated systems and services in place.\\

On the other hand, customers do not have an effective way to find and compare auto repair shops.
Currently, one of the only ways to compare repair shops is by manually searching or reaching out to
repair shops one-by-one. This process can often be repetitive and time-consuming.

The purpose of this project is to connect auto shops with vehicle owners (customers). This project
will allow independent auto repair shops and vehicle owners to interact in a more efficient and
effective manner. Vehicle owners will be able to search for auto repair shops and services based on
a variety of search filters; request quotes for service; book, view, and manage service
appointments. On the application, auto repair shop owners will have full shop management
capabilities such as: adding and managing a list of employees; managing a list of service types and
corresponding service appointment availabilities; managing store information such as location,
hours of operation, and contact information. Auto repair shop owners and employees will be able to
manage quotes, service appointments, and work orders from a single application. Ultimately, Sayyara
will significantly improve the auto repair experience for both independent auto repair shops and
vehicle owners.

\subsection{Inputs and Outputs}
\subsubsection{Inputs}
\begin{enumerate}
	\item Auto repair shop account details including shop name, shop owner first and last name, address,
	      phone number, email, password, and hours of operation
	\item Auto repair shop employee accounts including employee first and last name, phone number, email,
	      password
	\item Shop id given to an employee which is needed for employee to sign up and be associated with the
	      auto shop
	\item Customer information including full name, phone number, email, and password
	\item List of available services for each auto repair shop, along with details for each service such as
	      service type, type of parts used {(i.e., OEM, used, etc)}
	\item Schedule of availability for auto repair shops
	\item Quote request details including car make and model, problem description, images
	\item Selected time slot for service appointments
	\item Estimate information including price and estimated time
	\item Work order information including assigned employees, estimated time, progress, parts used, cost of
	      labour and parts, digital vehicle inspection {(DVI)} reports, warranty information, and odometer
	      reading
	\item Chat messages between auto repair shop and customers
	\item Search keywords for filtering service providers
	\item Customer's location for searching and filtering for nearby auto repair shops
	\item {[Stretch Goal]} Payment options for auto repair shop account subscriptions
\end{enumerate}
\subsubsection{Outputs}
\begin{enumerate}
	\item Profile view for auto repair shop and employee accounts
	\item View of appointments for shop owners and employees
	\item View of quote request for shop owners and employees
	\item View of appointments for customers
	\item View of quote request submitted for customers
	\item List of auto repair shops based on search keywords and filters inputted by customers
	\item View of work orders and corresponding details for shop owners and employees
	\item View of work orders, corresponding details, and progress updates for customer
	\item Chat view for both auto repair shops, employees and customers
	\item {[Stretch Goal]} Notifications to auto repair shops when a quote request is received
	\item {[Stretch Goal]} Notifications to vehicle owners when a quote is received, work is completed/assigned,
	      or an appointment has been created or updated
	\item {[Stretch Goal]} View of added payment options for auto repair shop subscription
\end{enumerate}

\subsection{Stakeholders}
\begin{itemize}
	\item Vehicle owners
	\item Auto repair shop owner
	\item Auto repair shop employees
	\item Sayyara (the company)
	\item Nabeel Ibrahim (project supervisor)
	\item Tiny Coders (developers of the project)
\end{itemize}

\subsection{Environment}
\subsubsection{Hardware}
\begin{itemize}
	\item The application will be supported for desktops, laptops, tablets and mobile devices.
\end{itemize}
\subsubsection{Software}
\begin{itemize}
	\item The application will be supported on Google Chrome and Microsoft Edge.
	\item The application will be supported on Windows and macOS.
	\item The application will be supported on Android and iOS mobile devices and tablets.
\end{itemize}

\section{Goals}
\subsection{Shop Management}
\begin{itemize}
	\item Allow shop owner to manage list of employees.
	\item Allow shop owner to manage shop details such as list of services, service appointment availability,
	      location, and contact details.
\end{itemize}

\subsection{Work Orders}
\begin{itemize}
	\item Allow shop owners to easily create, update, view, filter, and search work orders. Work orders will
	      include any details such as estimated time, parts used, and costs related to the work order and the
	      employees assigned. This will allow shop owners and employees to see details related to the work
	      orders and update any information if needed.
\end{itemize}

\subsection{Quotes}
\begin{itemize}
	\item Allow shop owners to give efficiently quotes to customer requests. The shop owners will be able to
	      chat with the vehicle owners and respond to requests easily through the application asynchronously.
	\item Allow vehicle owners to request a quote on their job to various auto shops at once. This will allow
	      vehicle owners to easily get quotes from multiple mechanics and compare prices to find the most
	      suitable shop.
\end{itemize}

\subsection{Appointments}
\begin{itemize}
	\item Allow shop owners to create, view, and edit appointments details. They can set their availability
	      on their calendar and view their scheduled appointments. This will make the booking appointment
	      process automated and reduce the amount of admin work on their end.
	\item Allow vehicle owners to search for auto shops and book an appointment at available auto shops. They
	      can select the time and date when they are available and schedule a time with an auto shop that is
	      available during that time. This will enable customers to book appointments at the selected auto
	      shop asynchronously.
\end{itemize}

\section{Stretch Goals}
\begin{itemize}
	\item Deploy application and server to the cloud.
	\item Have a notification system to notify when a quote has been requested, when appointments are created
	      or updated, and when a service job is completed/assigned to an employee.
	\item Include a reviews component to create reviews and view auto shop reviews. This way customers can
	      see past reviews before determining if they want to book an appointment with a specific shop.
	\item Include payment options for auto repair shop subscriptions. For the initial version of the
	      application, auto repair shops will not be required to enter a payment options as the application
	      will be under a free trial period.
\end{itemize}

\end{document}
