\documentclass[12pt, titlepage]{article}

\usepackage{amsmath, mathtools}
\usepackage[round]{natbib}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{colortbl}
\usepackage{xr}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{xfrac}
\usepackage{tabularx}
\usepackage{float}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage[section]{placeins}
\usepackage{caption}
\usepackage{fullpage}
\usepackage{array}
\usepackage[nottoc,numbib]{tocbibind}

\hypersetup{
	bookmarks=true,         % show bookmarks bar?
	colorlinks=true,        % false: boxed links; true: colored links
	linkcolor=red,          % color of internal links (change box color with linkbordercolor)
	citecolor=blue,         % color of links to bibliography
	filecolor=magenta,      % color of file links
	urlcolor=cyan           % color of external links
}


\externaldocument{../../SRS/SRS}

\input{../../Comments}
\input{../../Common}

\begin{document}

\title{Module Interface Specification for \progname{}}

\author{\authname}

\date{\today}

\maketitle

\pagenumbering{roman}

\section{Revision History}

\begin{table}[hp]
	\caption{Revision History} \label{TblRevisionHistory}
	\begin{tabularx}{\textwidth}{llX}
		\toprule
		\textbf{Date}     & \textbf{Developer(s)} & \textbf{Change}         \\
		\midrule
		December 28, 2022 & Arkin Modi            & Create Revision History \\
		January 7, 2023   & Joy Xiao              & Introduction            \\
		January 9, 2023   & Arkin Modi            & Add Module Hierarchy    \\
		\bottomrule
	\end{tabularx}
\end{table}

~\newpage

\section{Symbols, Abbreviations and Acronyms}

See SRS Documentation at
\url{https://github.com/arkinmodi/project-sayyara/blob/main/docs/SRS/SRS.pdf}

\wss{Also add any additional symbols, abbreviations or acronyms}

\begin{tabular}{l l}
	\toprule
	\textbf{symbol} & \textbf{description}            \\
	\midrule
	\progname       & Explanation of program name     \\
	MIS             & Module Interface Specifications \\
	MG              & Module Guide                    \\
	\bottomrule
\end{tabular}

\newpage

\tableofcontents

\newpage

\listoftables

\listoffigures

\newpage

\pagenumbering{arabic}

\section{Introduction}

The following document details the Module Interface Specifications for project Sayyara. Sayyara is
a progressive web application (PWA) which will act as a single platform for independent auto repair
shops and vehicle owners. This platform will allow independent auto repair shops and vehicle owners
to interact in a more efficient and effective manner. Vehicle owners can search for auto repair
shops and services; request quotes for service; book, view, and manage service appointments. On the
application, auto repair shop owners will be able to manage a list of employees; manage a list of
service types and corresponding service appointment availabilities; manage store information such
as location, hours of operation, and contact information. Auto repair shop owners and employees
will be able to manage quotes, service appointments, and work orders from a single application. The
MIS will detail specifications for the project described above.

Complementary documents include the System Requirement Specifications and Module Guide. The full
documentation and implementation can be found at
\url{https://github.com/arkinmodi/project-sayyara/}.

\section{Notation}

\wss{You should describe your notation.  You can use what is below as
	a starting point.}

The structure of the MIS for modules comes from \citet{HoffmanAndStrooper1995}, with the addition
that template modules have been adapted from \cite{GhezziEtAl2003}. The mathematical notation comes
from Chapter 3 of \citet{HoffmanAndStrooper1995}. For instance, the symbol := is used for a
multiple assignment statement and conditional rules follow the form $(c_1 \Rightarrow r_1 | c_2
	\Rightarrow r_2 | ... | c_n \Rightarrow r_n )$.

The following table summarizes the primitive data types used by \progname.

\begin{center}
	\renewcommand{\arraystretch}{1.2}
	\noindent
	\begin{tabular}{l l p{7.5cm}}
		\toprule
		\textbf{Data Type} & \textbf{Notation} & \textbf{Description}                                             \\
		\midrule
		character          & char              & a single symbol or digit                                         \\
		integer            & $\mathbb{Z}$      & a number without a fractional component in (-$\infty$, $\infty$) \\
		natural number     & $\mathbb{N}$      & a number without a fractional component in [1, $\infty$)         \\
		real               & $\mathbb{R}$      & any number in (-$\infty$, $\infty$)                              \\
		\bottomrule
	\end{tabular}
\end{center}

\noindent
The specification of \progname \ uses some derived data types: sequences, strings, and
tuples. Sequences are lists filled with elements of the same data type. Strings
are sequences of characters. Tuples contain a list of values, potentially of
different types. In addition, \progname \ uses functions, which
are defined by the data types of their inputs and outputs. Local functions are
described by giving their type signature followed by their specification.

\section{Module Decomposition}

The following table is taken directly from the Module Guide document for this project.

\begin{table}[H]
	\centering
	\begin{tabular}{p{0.3\textwidth} p{0.6\textwidth}}
		\toprule
		\textbf{Level 1}                                      & \textbf{Level 2}           \\
		\midrule

		Hardware-Hiding Module                                & ~                          \\

		\midrule

		\multirow{8}{0.3\textwidth}{Behaviour-Hiding Module}  & Users Module               \\
		                                                      & Quotes Module              \\
		                                                      & Appointments Module        \\
		                                                      & Work Orders Module         \\
		                                                      & Employee Management Module \\
		                                                      & Services Module            \\
		                                                      & Shop Lookup Module         \\
		                                                      & Shop Profile Module        \\
		\midrule

		\multirow{1}{0.3\textwidth}{Software Decision Module} & Database Driver Module     \\

		\bottomrule
	\end{tabular}
	\caption{Module Hierarchy}
	\label{TblMH}
\end{table}

\newpage

\section{MIS of \wss{Module Name}} \label{Module} \wss{Use labels for
	cross-referencing}

\wss{You can reference SRS labels, such as R\ref{R_Inputs}.}

\wss{It is also possible to use \LaTeX{} for hypperlinks to external documents.}

\subsection{Module}

\wss{Short name for the module}

\subsection{Uses}

\subsection{Syntax}

\subsubsection{Exported Constants}

\subsubsection{Exported Access Programs}

\begin{center}
	\begin{tabular}{p{2cm} p{4cm} p{4cm} p{2cm}}
		\hline
		\textbf{Name}    & \textbf{In} & \textbf{Out} & \textbf{Exceptions} \\
		\hline
		\wss{accessProg} & -           & -            & -                   \\
		\hline
	\end{tabular}
\end{center}

\subsection{Semantics}

\subsubsection{State Variables}

\wss{Not all modules will have state variables.  State variables give the module
	a memory.}

\subsubsection{Environment Variables}

\wss{This section is not necessary for all modules.  Its purpose is to capture
	when the module has external interaction with the environment, such as for a
	device driver, screen interface, keyboard, file, etc.}

\subsubsection{Assumptions}

\wss{Try to minimize assumptions and anticipate programmer errors via
	exceptions, but for practical purposes assumptions are sometimes appropriate.}

\subsubsection{Access Routine Semantics}

\noindent \wss{accessProg}():
\begin{itemize}
	\item transition: \wss{if appropriate}
	\item output: \wss{if appropriate}
	\item exception: \wss{if appropriate}
\end{itemize}

\wss{A module without environment variables or state variables is unlikely to
	have a state transition.  In this case a state transition can only occur if
	the module is changing the state of another module.}

\wss{Modules rarely have both a transition and an output.  In most cases you
	will have one or the other.}

\subsubsection{Local Functions}

\wss{As appropriate} \wss{These functions are for the purpose of specification.
	They are not necessarily something that is going to be implemented
	explicitly.  Even if they are implemented, they are not exported; they only
	have local scope.}

\newpage

\bibliographystyle{plainnat}
\bibliography{../../../refs/References}

\newpage

\section{Appendix}

\wss{Extra information if required}

\end{document}
